Misperceptions Regarding Women's Employment Outside the Home and Their Impact on Women in Saudi Arabia

### 2024-02-14 outputs/paper/paper.qmd
final improvement

---
title: "Misperceptions Regarding Women's Employment Outside the Home and Their Impact on Women in Saudi Arabia"
author: 
  - Boxuan Yi
  - Ruoxian Wu
thanks: "Code and data are available at: https://github.com/ScarletWu/Misperceived-Social-Norms-Women-Working-Outside-the-Home-in-Saudi-Arabia. Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1557/. The original paper and its replicated package can be found here: https://www.aeaweb.org/articles?id=10.1257/aer.20180975."
date: "February 12, 2024"
date-format: long
abstract: "Husbands who hold guardianship and discourage their wives from working outside the home are often perceived as the main reason for the low female workforce participation in Saudi Arabia. We use data and surveys from the American Economic Association to analyze this perception, revealing that a majority of young husbands in Saudi Arabia privately support women working outside the home but underestimate the support of other men. This paper also discusses the positive effects brought about by correcting this misperception, strategies for reducing information intervention, and the unusual Saudi female employment rate during the pandemic."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

# Data
## Source
The paper used for replication is from American Economic Association, American Economic Review. The replication package is downloaded from Misperceived Social Norms: Women Working Outside the Home in Saudi Arabia webpage, under Additional Materials.

Our reproduction seeks to address two findings written in the original paper, using results they collected from the main experiment, its follow-up and online survey.

>>>>

---
title: "Misperceptions Regarding Women's Employment Outside the Home and Their Impact on Women in Saudi Arabia"
author: 
  - Boxuan Yi
  - Ruoxian Wu
thanks: "Code and data are available at: https://github.com/ScarletWu/Misperceived-Social-Norms-Women-Working-Outside-the-Home-in-Saudi-Arabia. Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1557/. The original paper and its replicated package can be found here: https://www.aeaweb.org/articles?id=10.1257/aer.20180975."
date: "February 12, 2024"
date-format: long
abstract: "Husbands who hold guardianship and discourage their wives from working outside the home are often perceived as the main reason for the low female workforce participation in Saudi Arabia. This paper analyzes this common perception, revealing that a majority of young husbands in Saudi Arabia privately support women working outside the home but underestimate the support of other men. This paper also discusses the positive effects brought about by correcting this misperception, strategies for reducing information intervention, and the unusual Saudi female employment rate during the pandemic."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

# Data
## Source
The replication package is obtained from 'Misperceived Social Norms: Women Working Outside the Home in Saudi Arabia', a paper from American Economic Association [@MisperceivedSocialNorm]. Our reproduction seeks to address two findings written in the original paper, using results authors collected through the main experiment, follow-up, an online survey, and the programming language R [@r].
